---
title: "ProdPad Tag Roundup"
output: 
  html_document:
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`r if(Sys.getenv('PRODPAD_TAG') == '') { "<h4>ERROR: You must set the PRODPAD_TAG environment variable</h4>\n" }`
`r if(Sys.getenv('PRODPAD_API_KEY') == '') { "<h4>ERROR: You must set the PRODPAD_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('PRODPAD_API_KEY') == '' || Sys.getenv('PRODPAD_TAG') == '') { knitr::knit_exit() }`

## ``r Sys.getenv('PRODPAD_TAG')`` Tag Report {.tabset}

```{r include=FALSE}
library(dplyr)
library(prodpad)
library(tidyr)
library(reactable)

pcli <- prodpad()

roughstuff <- get_feedback(pcli, tags = Sys.getenv('PRODPAD_TAG'), product = "RStudio Connect")

rsdf <- roughstuff %>%
  rename(fid = id, logged = created_at) %>%
  select(fid, feedback, logged, customer) %>%
  tidyr::unnest_wider(customer) %>%
  select(name, feedback, logged, fid) %>%
  rename(customer = name)

lsdf <- roughstuff %>%
  rename(fid = id) %>%
  select(fid, tags) %>%
  tidyr::unnest_longer(tags) %>%
  tidyr::hoist(tags, tag_name = "tag")
```


```{r message=FALSE, warning=FALSE, include=FALSE}
tags_tbl <- roughstuff %>%
  rename(fid = id) %>%
  select(fid, tags) %>%
  tidyr::unnest_longer(tags) %>%
  tidyr::hoist(tags, tag_name = "tag")

ideas_tbl <- roughstuff %>%
  rename(fid = id) %>%
  select(fid, ideas) %>%
  tidyr::unnest_longer(ideas) %>%
  tidyr::hoist(ideas, iid = "id")


getidea <- function(.x) {
  get_idea(pcli, .x)
}

library(purrr)

ideas_tbl2 <- ideas_tbl %>%
  mutate(idea = map(iid, possibly(getidea, NA)))

ideas_tbl3 <- ideas_tbl2 %>%
  tidyr::hoist(idea, 
               link = "web_url",
               title = "title") %>%
  select(iid, fid, link, title)
```

### Feedback from the `r Sys.getenv('PRODPAD_TAG')` Tag

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(stringr)

tags_lookup <- function(table, lid){
  table %>% filter(fid == lid) %>%
    select(tag_name)
}

ideas_lookup <- function(table, lid){
  table %>% filter(fid == lid) %>%
    select(title, link)
}

reactable(rsdf, details = function(index) {
    ftags <- tags_lookup(lsdf, rsdf[index,]$fid)
    reactable(data.frame(ftags), fullWidth = FALSE, 
              columns = list(tag_name = colDef(name = "Linked Tags", minWidth = 150))
              )
},
searchable = T,
highlight = T,
columns = list(
  fid = colDef(name = "ID"),
  feedback = colDef(name = "Feedback", html = T, minWidth = 500, details = function(index){
    fideas <- ideas_lookup(ideas_tbl3, rsdf[index,]$fid)
    aid <- str_replace_na(as.vector(fideas$title))
    paste("Linked Ideas: ", str_c(aid, collapse = ", "))
  }),
  logged = colDef(name = "Date", format = colFormat(date = T)),
  customer = colDef(name = "Requester")
)
)


```

### Related Tags

ProdPad Feedback is often associated with more than one tag. This summary shows frequency counts for tags that have been used in addition to `r Sys.getenv('PRODPAD_TAG')`.

```{r echo=FALSE, message=FALSE, warning=FALSE}

reltags <- plyr::count(lsdf, 'tag_name') %>%
  arrange(desc(freq))

reactable(reltags, defaultPageSize = 14, columns = list(
  tag_name = colDef(name = "Tag Name"),
  freq = colDef(name = "Frequency Count")
))
```

### Related Ideas

ProdPad Feedback is often associated with one or more Ideas. This summary shows frequency counts for Ideas that have been linked to Feedback under the `r Sys.getenv('PRODPAD_TAG')` tag.

```{r echo=FALSE, message=FALSE, warning=FALSE}

relide <- ideas_tbl3 %>%
  drop_na %>%
  mutate(link_title = paste('<a href="',link,'">',title,'</a>', sep = "")) %>%
  plyr::count(., 'link_title') %>%
  arrange(desc(freq))

reactable(relide, defaultPageSize = 14, columns = list(
  link_title = colDef(name = "Idea Title", html = T),
  freq = colDef(name = "Frequency Count")
))
```

### Feedback Over Time

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summary of feedback counts by year and month

library(lubridate)

fcounts <- rsdf %>%
  mutate(date = ymd_hms(logged), month = format(date, "%m"), year = format(date, "%Y")) %>%
  group_by(month, year) %>%
  tally() %>%
  arrange(desc(year), desc(month))

reactable(fcounts, defaultPageSize = 12, columns = list(
  month = colDef(name = "Month"),
  year = colDef(name = "Year"),
  n = colDef(name = "Feedback Count")
))
```
